---
output:
  md_document:
    variant: gfm
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<a id="devex-badge" rel="Inspiration" href="https://github.com/BCDevExchange/assets/blob/master/README.md"><img alt="An idea being explored and shaped. Open for discussion, but may never go anywhere." style="border-width:0" src="https://assets.bcdevexchange.org/images/badges/inspiration.svg" title="An idea being explored and shaped. Open for discussion, but may never go anywhere." /></a>

[![Travis build status](https://travis-ci.org/bcgov/geometr.svg?branch=master)](https://travis-ci.org/bcgov/geometr)



# geometr

An R package to query Environment and Climate Change Canada's GeoMet webservices

## Project Status

This package is maintained by the Knowledge Management Branch of the [British Columbia Ministry of Environment and Climate Change Strategy](https://www2.gov.bc.ca/gov/content/governments/organizational-structure/ministries-organizations/ministries/environment-climate-change). This project is under construction is not stable for any kind of sustained use.

### Features

- Currently the hydrometric historical webservice is the only data available through this service

### Installation
```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("bcgov/geometr")
```

### Usage
First we have to load the package
```{r}
library(geometr)
```

The collections current supported by the geomet webservice are (as of `r Sys.Date()`):
```{r}
collections <- geomet_collection()

collections[,c("title", "name")]
```

For instance daily mean value can be queried using:
```{r}
geomet_daily_mean(station_number = "08MF005")
```


### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/geometr/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2018 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
